%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%
% Adapted from https://github.com/dartar/cvtex
% by David V. Smith (david.v.smith@temple.edu)
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, letterpaper]{article}
\usepackage{xunicode,fontspec,xltxtra} 
\usepackage{libertine} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{letterpaper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{color}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}} % need this by every paper so i don't have to worry about the link breaking
\newcommand{\psyarxiv}[1]{\href{#1}{\textit{PsyArXiv}}}
\newcommand{\biorxiv}[1]{\href{#1}{\textit{bioRxiv}}}
\newcommand{\medrxiv}[1]{\href{#1}{\textit{medRxiv}}}

% -- "open science" made explicit 
\newcommand{\neurovault}[1]{\href{#1}{\scriptsize\textsc{[NeuroVault]}}}
\newcommand{\materials}[1]{\href{#1}{\scriptsize\textsc{[Open Materials]}}}
\newcommand{\data}[1]{\href{#1}{\scriptsize\textsc{[Open Data]}}}
\newcommand{\preregistration}[1]{\href{#1}{\scriptsize\textsc{[PreRegistration]}}}

% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\LARGE}
\subsectionfont{\mdseries\scshape\large\bfseries} 
\subsubsectionfont{\mdseries\upshape\large} 

\sectionfont{\sectionrule{0pt}{0pt}{-5pt}{0.8pt}}


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[driverfallback=dvipdfm, bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={David V. Smith - vita},
	pdfauthor={David V. Smith},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue} 


% IMPORT OTHER PACKAGES, INCLUDING PYTHONTEX
\usepackage{amsmath,amssymb}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{url}
\urlstyle{same}
\usepackage{academicons}
\usepackage{hanging}
\usepackage{multicol}
\usepackage{enumitem}
\defaultfontfeatures{Extension = .otf}
% \usepackage{fontawesome}
\usepackage[makestderr]{pythontex}
\restartpythontexsession{\thesection}
\usepackage[framemethod=TikZ]{mdframed}
\newcommand{\pytex}{Python\TeX}
\usepackage{nameref}

\usepackage{fontawesome6}  % FA6 Free
% If you own FA6 Pro desktop fonts and use XeLaTeX/LuaLaTeX:
% \usepackage[pro]{fontawesome6}




\usepackage{pgf,interval}

\usepackage{lipsum}
\usepackage{fancyhdr}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rhead{\today}

% START DOCUMENT
\begin{document}
\thispagestyle{fancy}
\textbf{{\Huge David V. Smith, Ph.D.}} \\[.2cm]
\begin{tabbing}
Associate Professor \hspace{2.25in} \= \aiGoogleScholar \hspace{.2cm} \= \href{https://scholar.google.com/citations?user=czV7OcQAAAAJ&hl=en}{scholar.google.com} \\ 
Department of Psychology \& Neuroscience  \> \aiResearchGate \> \href{https://www.researchgate.net/profile/David_Smith96/}{researchgate.net} \\
Temple University \> \faGithub \>  \href{https://github.com/DVS-Lab/}{github.com/DVS-Lab} \\
825 Weiss Hall \> \aiOrcid \> \href{https://orcid.org/0000-0001-5754-9633}{orcid.org/0000-0001-5754-9633} \\
1701 North 13th Street \>  \aiPublons \> \href{https://publons.com/author/1204254/david-v-smith}{publons.com} \\
Philadelphia, PA, 19122 \> \aiOSF \> \href{https://osf.io/5zq6h/}{osf.io} \\[.2cm]
phone: 215-204-1552  \> \faBluesky \> \href{https://bsky.app/profile/dvsmith.bsky.social}{dvsmith.bsky.social} \\
email: \href{mailto:david.v.smith@temple.edu}{david.v.smith@temple.edu} \> {\faIcon{building-columns}} \> \href{https://sites.temple.edu/neuroeconlab/}{sites.temple.edu/neuroeconlab}
 \end{tabbing}


% or the squared logo:
% \faSquareBluesky


%%\hrule \section*{Professional Experience}
\section*{Professional Experience}
\begin{hangparas}{.5in}{1}

\years{2023-present} Associate Professor, Department of Psychology \& Neuroscience, Temple University.

\years{2023-present} Associate Director, Temple University Brain Research \& Imaging Center (TUBRIC).

\years{2022-2023} Assistant Professor, Department of Psychology \& Neuroscience, Temple University.

\years{2017-2022} Assistant Professor, Department of Psychology, Temple University.

\years{2012-2016} Postdoctoral Fellow, Department of Psychology, Rutgers University -- Newark.

\years{2006-2012} Graduate Student, Center for Cognitive Neuroscience, Duke University. \\

\end{hangparas}


%\hrule \section*{Education \& Training}
\section*{Education and Training}
\begin{tabbing}
\years{2012-2016}\textsc{PostDoc} \hspace{.75in} \= \textsc{Rutgers University -- Newark} \\
\> Department of Psychology \\
\> \textsc{Advisor}: Dr. Mauricio Delgado \\ [.2cm]

\years{2012}\textsc{Ph.D.} \> \textsc{Duke University} \\
\> Department of Psychology \& Neuroscience \\
\> \textsc{Advisor}: Dr. Scott Huettel \\ [.2cm]

\years{2006}\textsc{B.S.} \> \textsc{University of South Carolina} \\
\> Experimental Psychology, \textit{Magna Cum Laude} \\
\> \textsc{Advisors}: Drs. Gordon Baylis \& Chris Rorden
 \end{tabbing}


%\hrule \section*{Honors \& Awards}
\section*{Honors and Awards}
\noindent
\years{2025}Presidential Faculty Award, College of Liberal Arts, Temple University \\
\years{2025}Fellow, Association for Psychological Science\\
\years{2022}Open \& Reproducible Science Award, Society for Social Neuroscience\\
\years{2022}Training Fellowship, ReproNim / International Neuroinformatics Coordinating Facility (INCF)\\
\years{2021}College of Liberal Arts Research Award, Temple University\\
\years{2019}Excellence in Mentoring, Temple University, Department of Psychology Honors Program\\
\years{2019}Faculty Fellow, Public Policy Lab, Temple University\\
\years{2016}Rising Star, Association for Psychological Science\\
\years{2016}Young Investigator Travel Award, NIDA Symposium on Persistent Maladaptive Behaviors\\
\years{2016}NIDA Director’s Travel Award, The College on Problems of Drug Dependence\\
\years{2015}Ruth L. Kirschstein Postdoctoral National Research Service Award, NIMH\\
\years{2015}Merit Abstract Award, Organization for Human Brain Mapping\\
\years{2015}Travel Award, Scientific Research Network on Decision Neuroscience \& Aging\\
\years{2009}Ruth L. Kirschstein Predoctoral National Research Service Award, NIMH\\
\years{2010}Travel Award, Organization for Human Brain Mapping\\
\years{2009}Fellow, Summer Institute in Cognitive Neuroscience, UC - Santa Barbara\\
\years{2008}Fellow, CIT Flexible Learning Space, Duke University\\
\years{2007}Travel Award, Organization for Human Brain Mapping\\
\years{2006}Roger Black Award for Psychological Research, University of South Carolina\\
\years{2005}\textit{Phi Beta Kappa}, University of South Carolina\\
\years{2005}Fellow, NSF Summer Research Institute, University of South Carolina\\
\years{2005}Stubbs Scholar, University of South Carolina\\
\years{2004}Phi Beta Kappa Freshman Scholar Award, University of South Carolina\\
\years{2004}Baroody Scholar Award, University of South Carolina\\
\years{2003}Abney Scholar, University of South Carolina\\
\years{2002}LIFE Scholarship, University of South Carolina


%\hrule \section*{Extramural Funding}

\section*{Grants as Principal Investigator}
[*approximate total costs; †approximate direct costs]
\subsection*{Active}
\begin{hangparas}{.5in}{1}

\years{2021-2026} Social Reward Processing Across the Lifespan: Identifying Risk Factors for Financial Exploitation. (NIH R01-AG067011; *\$3,419,480). Principal Investigator, with Co-Is Giovannetti, Jarcho, and Olson.

\years{2024-2026} Social Reward Processing Across the Lifespan: Identifying Risk Factors for Financial Exploitation Diversity Supplement. (NIH 3R01AG067011-02S1; *\$120,411). Diversity Supplement supporting Melanie Kos. \\

\end{hangparas}

\subsection*{Pending}
\begin{hangparas}{.5in}{1}

\years{2026-2028} Environmental and Neural Drivers of Internalizing and Externalizing Behaviors. (NIH R21-MH000000 *\$432,217). Principal Investigator, with MPI Mennis and Co-I Olino. [Submitted June 2025]

\years{2026-2028} Modifiable and Nonmodifiable Risk Factors for Financial Exploitation and Subjective Cognitive Decline. (NIH R03-AG098465 *\$158,500). Principal Investigator, with Co-Is Mennis and Helion. [Submitted February 2025]

\years{2025-2029} Environmental and Neural Drivers of Adolescent Cannabis Use. (NIH R01-DA062153 *\$2,453,968). Principal Investigator, with MPI Mennis and Co-Is Olino and Weinstein. [Submitted November 2024]

\years{2025-2030} Modulating Reward Processing with Transcranial Electrical Stimulation. (NIH R01-DA063106; *\$3,902,693). Principal Investigator, with MPI Krekelberg and Co-Is Alloy and Weinstein. [Submitted August 2024] \\

\end{hangparas}



\subsection*{Completed}
\begin{hangparas}{.5in}{1}

\years{2019-2021} Aberrant Reward Sensitivity: Mechanisms Underlying Substance Use. (NIH R03-DA046733; *\$225,000). Principal Investigator, with Co-Is Alloy, Jarcho, McCloskey, and Chein.

\years{2017-2021} Remote Modulation of Reward Circuits with Noninvasive Brain Stimulation. (NIH R21-MH113917; *\$420,000). Principal Investigator, with Co-I Krekelberg.

\years{2018-2019} Modulating Individual Differences in Reward Sensitivity with Transcranial Current Stimulation. Targeted Small Grant Award from the Office of the Vice President for Research at Temple University; †\$10,000). Principal Investigator, with Co-I Reilly.

\years{2017-2018} Social Reward and Aging: Identifying the Neural Underpinnings of Peer Influences. Pilot Grant from the Scientific Research Network on Decision Neuroscience \& Aging; †\$30,000). Principal Investigator, with Co-Is Fareri, Giovannetti, and Reeck. [Subaward of NIH R24-AG054355 (PI Samanez-Larkin)]

\years{2015-2016} Parsing Reward: Identifying Distinct Neural Pathways for Specific Reward Properties. (NIH F32-MH107175; †\$110,000). Principal Investigator.

\years{2009-2012} Neurobiological Underpinnings of Decision Making. (NIH F31-MH086248; †\$82,000). Principal Investigator. \\
\end{hangparas}


%% CO-I/CONSULTANT GRANTS
\section*{Grants as Co-Investigator or Consultant}
[*approximate total costs; †approximate direct costs]
\subsection*{Active}
\begin{hangparas}{.5in}{1}

\years{2025-2026} Modulating reward-based learning in older adults using transcranial electrical stimulation. Pilot Grant from the Scientific Research Network on Decision Neuroscience \& Aging; *\$24,000). Co-Investigator, with PI James Wyngaarden. [Subaward of NIH R24-AG076847 (PIs Seaman and Lighthall)]

\years{2022-2027} The influence of mesolimbic-hippocampal interactions on episodic memory during active information seeking. (NIH R01-DA055259; *\$2,821,807). Co-Investigator, with PI Vishnu Murty (University of Oregon). \\

\end{hangparas}

\subsection*{Pending}
\begin{hangparas}{.5in}{1}
\years{2024-2029} Improving decision-making under uncertainty through emotion regulation. (NIH R01; *\$1,810,704). Co-Investigator, with PI Chelsea Helion (Temple University).

\years{2023-2028} Ultraprocessed food addiction, hunger, and the frontal pole/medial orbitofrontal cortex in young adults. (NIH R01; *\$3,691,273). Co-Investigator, with PI Eunice Chen (Temple University).

\years{2023-2028} An inverse developmental gradient of cerebellar modulation of social behavior. (NIH R01 *\$2,555,330) Co-Investigator, with PI Ingrid Olson (Temple University).

\years{2022-2027} Anhedonia-related deficits in context-sustained goal pursuit across normative and clinical-risk populations. (NIH R01 *\$2,922,995) Co-Investigator, with PI Vishnu Murty (University of Oregon). \\


\end{hangparas}

\subsection*{Completed}
\begin{hangparas}{.5in}{1}
\years{2020-2024} The role of social support and close relationships on neural and behavioral computations of value. (NIH R15-MH122927; *\$389,000). Consultant, with PI Dominic Fareri (Adelphi University).

\years{2018-2021} Social Reward Learning in Schizophrenia. (NIH R21-MH116422; †\$275,000). Consultant, with PI Pamela Butler (Nathan Kline Institute).

\years{2019-2021} Pupillometry as a Physiological Biomarker for Preclinical Dementia in Minority Aging. (Alzheimer’s Disease Administrative Supplement for NIH R01-DC013063; *\$388,000). Co-Investigator, with PI Reilly (Temple University). \\

\end{hangparas}



% PUBLICATIONS
\section*{Bibliography}
\aiGoogleScholar \hspace{.01cm} \href{https://scholar.google.com/citations?user=czV7OcQAAAAJ&hl=en}{scholar.google.com}: h-index: 30; i10-index: 52; total citations: 5554 \\ 
\lbrack*co-first authors; †trainee under my supervision; \^{}co-senior authors] \\ 

\textit{Where possible, I include links to \href{https://neurovault.org}{NeuroVault} maps, open materials, open data, and preregistrations.}


\subsection*{Preprints Under Review}

\begin{hangparas}{.5in}{1}

Wyngaarden JB, Nambiar A, Dennison J, Alloy LB, Fareri DS, Jarcho JM, \textbf{Smith DV}. Trait reward sensitivity and behavioral motivation shape connectivity between the default mode network and the striatum during reward anticipation. \biorxiv{https://doi.org/10.1101/2025.04.17.649386}

Yang Y† \& \textbf{Smith DV}. Structure-Trait-Identity Relation (STIR): An Integrative Framework for Understanding Redistribution Decisions in Economic Games. Preprint available on \psyarxiv{https://osf.io/preprints/psyarxiv/43nvt}

Shen X†, Wang KS, Murty VP, Delgado MR, \textbf{Smith DV}. Differential representations for affective and informative components of reward in the striatum and hippocampus. Preprint available on \biorxiv{https://doi.org/10.1101/2024.09.20.614186}. \materials{https://github.com/KarenShen21/ru-highres}. \preregistration{https://aspredicted.org/DKZ_W5Y}

\textbf{Smith DV}*, Zaff O*, Wyngaarden JB†, Dennison JB†, Sazhin D†, Chein J, Alloy LB, McCloskey M, Jarcho JM, Fareri D. Social Closeness and Reward Sensitivity Enhance Corticostriatal Function during Experiences of Shared Rewards. Preprint available on \biorxiv{https://doi.org/10.1101/2023.10.19.562908}. \neurovault{https://neurovault.org/collections/15006/} \materials{https://github.com/DVS-Lab/istart-sharedreward} \data{https://openneuro.org/datasets/ds004920} \preregistration{https://aspredicted.org/blind.php?x=SFX_MXL} \\


\end{hangparas}

\subsection*{Peer-Reviewed Journal Articles}

\begin{hangparas}{.5in}{1}

[69] Tropea T†, Yang Y†, Ludwig R, Fareri DS, Mennis J, \& \textbf{Smith DV} (2025). Reduced community-level social cohesion is associated with higher risk for financial exploitation. \textit{Aging and Mental Health}, 1-14. \doi{https://doi.org/10.1080/13607863.2025.2533493} \preregistration{https://doi.org/10.17605/OSF.IO/86XHK}

[68] Mattoni M, \textbf{Smith DV}, Chein J, \& Olino TM. (2025). Functional connectivity heterogeneity and consequences for clinical and cognitive prediction: Stage 2 registered report. \textit{Imaging Neuroscience}, 3, IMAG.a.107. \doi{https://doi.org/10.1162/IMAG.a.107}

[67] Yang Y†, Hackett K, Katta S†, Ludwig R†, Jarcho J, Giovannetti T, Fareri DS\^{}, \textbf{Smith DV}\^{} (2025, in press). Psychological, social, and health-related factors predict risk for financial exploitation. \textit{Communications Psychology}, 3, 88. \doi{https://doi.org/10.1038/s44271-025-00266-x} \materials{https://osf.io/hd5nx/} \data{https://osf.io/hd5snx/} \preregistration{https://osf.io/hd5nx/}

[66] Sazhin D†, Dachs A†, \textbf{Smith DV} (2025). Meta-Analysis Reveals That Explore–Exploit Decisions Are Dissociable by Activation in the Dorsal Lateral Prefrontal Cortex, Anterior Insula, and Dorsal Anterior Cingulate Cortex. \textit{European Journal of Neuroscience}, 61(6), e70081. \doi{https://doi.org/10.1111/ejn.70081} \neurovault{https://neurovault.org/collections/15560/} \data{https://osf.io/86kp9/} \preregistration{https://aspredicted.org/7hc7c.pdf}

[65] Shen X† \& \textbf{Smith DV} (2024). Precision neuroimaging reveals corticostriatal mapping, \textit{Journal of Neurophysiology}, 32(6), 1744-1746. \doi{https://doi.org/10.1152/jn.00231.2024}

[64] Sazhin D†, Wyngaarden JB†, Dennison JB†, Zaff O†, Fareri D, McCloskey M, Alloy LB, Jarcho JM, \textbf{Smith DV} (2024). Trait Reward Sensitivity Modulates Connectivity with the Temporoparietal Junction and Anterior Insula during Strategic Decision Making. \textit{Biological Psychology}, 192, 108857. \doi{https://doi.org/10.1016/j.biopsycho.2024.108857} \neurovault{https://identifiers.org/neurovault.collection:15045} \materials{https://github.com/DVS-Lab/istart-ugdg} \data{https://openneuro.org/datasets/ds004920} \preregistration{https://aspredicted.org/55gd8.pdf} 

[63] Sazhin D†, Murty VP, Helion C, \textbf{Smith DV} (2024). A behavioral dataset of predictive decisions given trends in information across adulthood. \textit{Data in Brief}, 56, 110832. \doi{https://doi.org/10.1016/j.dib.2024.110832} \data{https://zenodo.org/doi/10.5281/zenodo.11513694}

[62] \textbf{Smith DV}, Sharp CJ, Dachs A, Wyngaarden J, Sazhin D, Yang Y, Kos M, Tropea T, Kohli I, Clithero JA., Olson I, Giovannetti T, Fareri D, Jarcho JM. (2024). Social Reward and Nonsocial Reward Processing Across the Adult Lifespan: An Interim Multi-echo fMRI and Diffusion Dataset. \textit{Data in Brief}, 56, 110810. \doi{https://doi.org/10.1016/j.dib.2024.110810} \data{https://doi.org/10.18112/openneuro.ds005123.v1.1.3}

[61] Dejoie JM, Senia N, Konova A, \textbf{Smith DV}, Fareri D (2024). Common and Distinct Drug Cue Reactivity Patterns Associated with Cocaine and Heroin: An fMRI Meta-Analysis. \textit{Imaging Neuroscience}, 2, 1-18. \doi{https://doi.org/10.1162/imag_a_00211}

[60] Halchenko Y, Goncalves M, Ghosh S, Velasco P, Castello M, Salo T, Wodder J, Hanke M, Sadil P, Gorgolewski K, Ioanas H, Rorden C, Hendrickson TJ, Dayan M, Houlihan SD, Kent J, Strauss T, Lee J, To I, Markiewicz CJ, Lukas D, Butler E, Thompson T, Termenon M, \textbf{Smith DV}, Macdonald A, Kennedy DN (2024). HeuDiConv — flexible DICOM conversion into structured directory layouts. \textit{Journal of Open Source Software}, 9(99), 5839. \doi{https://doi.org/10.21105/joss.05839}

[59] Wyngaarden JB†*, Johnston CR*, Sazhin D†, Dennison JB†, Zaff O†, Fareri D, McCloskey M, Alloy LB, \textbf{Smith DV}\^{}, Jarcho JM\^{} (2024). Corticostriatal Responses to Social Reward are Linked to Trait Reward Sensitivity and Subclinical Substance Use in Young Adults. \textit{Social Cognitive Affective Neuroscience}, 19(1): nsae033. \doi{https://doi.org/10.1093/scan/nsae033} \materials{https://github.com/DVS-Lab/istart-socdoors} \data{https://doi.org/10.18112/openneuro.ds004920.v1.1.0} \preregistration{https://aspredicted.org/blind.php?x=JNH_EGK} 

[58] \textbf{Smith DV}, Wyngaarden JB†, Sharp CJ†, Sazhin D†, Zaff O†, Fareri  DS, Jarcho JM (2024). An fMRI Dataset of Social and Nonsocial Reward Processing in Younger Adults. \textit{Data in Brief}, 53, 110197. \doi{https://doi.org/10.1016/j.dib.2024.110197} \materials{https://github.com/DVS-Lab/ISTART-DataInBrief} \data{https://doi.org/10.18112/openneuro.ds004920.v1.1.0} 

[57] \textbf{Smith DV}, Ludwig RM†, Dennison JB†, Reeck C, Fareri DS (2024). An fMRI Dataset on Social Reward Processing and Decision Making in Younger and Older Adults. \textit{Scientific Data}, 11(1). \doi{https://doi.org/10.1038/s41597-024-02931-y} \materials{https://github.com/DVS-Lab/srndna-datapaper} \data{https://doi.org/10.18112/openneuro.ds003745.v2.1.0}

[56] Shen X†, Helion C, \textbf{Smith DV}, Murty VP (2024). Motivation as a lens for understanding information-seeking behaviors. \textit{Journal of Cognitive Neuroscience}, 36(2), 362-376. \doi{https://doi.org/10.1162/jocn_a_02083}

[55] Helion C*, Ulichney V*, \textbf{Smith DV}, Jarcho J (2023). When thinking you are better leads to feeling worse: Self-other asymmetries in prosocial behavior and increased anxiety during the Covid-19 pandemic. \textit{PLoS One}, 18(9):e0291329. \doi{https://doi.org/10.1371/journal.pone.0291329} \materials{https://osf.io/hpv43/} \data{https://osf.io/hpv43/} \preregistration{https://aspredicted.org/blind.php?x=HGQ_8XB} 

[54] Dennison JB†, Tepfer LJ†, \textbf{Smith DV} (2023). Tensorial Independent Component Analyses Reveals Social and Reward Networks Associated with Major Depressive Disorder. \textit{Human Brain Mapping}, 44(7), 2905-20. \doi{https://doi.org/10.1002/hbm.26254} \neurovault{https://identifiers.org/neurovault.collection:13474} \materials{https://github.com/jbdenniso/CSNmaps} \preregistration{https://aspredicted.org/BIO_JHP}

[53] Mattoni M, \textbf{Smith DV}, Olino T (2023). Characterizing Heterogeneity in Early Adolescent Reward Networks and Individualized Associations with Behavioral and Clinical Outcomes. \textit{Network Neuroscience}, 7(2): 787–810. \doi{https://doi.org/10.1162/netn_a_00306} \preregistration{https://osf.io/6n5j2}

[52] Karvey YG, Helion C, Vafiadis A, \textbf{Smith DV}, Jarcho JM (2023). Stress, trauma, and perception of eating behavior changes during the first weeks of the COVID-19 outbreak. \textit{International Journal of Eating Disorders}, 56(1), 169-181. \doi{https://doi.org/10.1002/eat.23863} \preregistration{https://aspredicted.org/FTR_AIB}

[51] Shen X†, Houser T, \textbf{Smith DV}, Murty VP (2023). Machine-learning as a validated tool to characterize individual differences in free recall of naturalistic events. \textit{Psychonomic Bulletin \& Review}, 30, 308–316. \doi{https://doi.org/10.3758/s13423-022-02171-4}

[50] Dobryakova E \& \textbf{Smith DV} (2022). Reward Enhances Connectivity between the Ventral Striatum and the Default Mode Network. \textit{NeuroImage}, 285:119398. \doi{https://doi.org/10.1016/j.neuroimage.2022.119398} \neurovault{https://identifiers.org/neurovault.collection:10921} \materials{https://github.com/edobryakova/DobryakovaSmith_HCP}

[49] Allen K, Reardon J, Lu Y, \textbf{Smith DV}, Rainsford E, Walsh L (2022). Towards improving peer-review: Crowd-sourced insights from Twitter. \textit{Journal of University Teaching \& Learning}, 19(3):2. \doi{https://ro.uow.edu.au/jutlp/vol19/iss3/02}

[48] Fareri DS, Hackett K, Tepfer LJ†, Kelly V†, Henninger N, Reeck C, Giovannetti T, \textbf{Smith DV}  (2022). Age-Related Differences in Ventral Striatal and Default Mode Network Function During Reciprocated Trust. \textit{NeuroImage}, 256:119267. \doi{https://doi.org/10.1016/j.neuroimage.2022.119267} \neurovault{https://identifiers.org/neurovault.collection:10447} \materials{https://github.com/DVS-Lab/srndna-trustgame} \data{https://openneuro.org/datasets/ds003745} \preregistration{https://aspredicted.org/MVZ_ODI}

[47] Dennison JB†*, Sazhin D†*, \textbf{Smith DV} (2022). Decision Neuroscience and Neuroeconomics: Recent Progress and Ongoing Challenges. \textit{Wiley Interdisciplinary Reviews: Cognitive Science}, 13(3):e1589. \doi{https://doi.org/10.1002/wcs.1589}

[46] O'Shea IM, Popal H, Olson IR, Murty VP\^{}, \textbf{Smith DV}\^{} (2022). Distinct Alterations in Cerebellar Connectivity with Substantia Nigra and Ventral Tegmental Area in Parkinson's Disease. \textit{Scientific Reports}, 12, 3289. \doi{https://doi.org/10.1038/s41598-022-07020-x} \preregistration{https://aspredicted.org/WAQ_SVQ}

[45] Jarcho JM, Wyngaarden JB†, Johnston CR, Quarmley M, \textbf{Smith DV}, Cassidy CM (2022). Substance Abuse in Emerging Adults: The Role of Neuromelanin and Ventral Striatal Response to Social and Monetary Rewards. \textit{Brain Sciences}, 12(3):352. \doi{https://doi.org/10.3390/brainsci12030352}

[44] Shen X†, Ballard IC, \textbf{Smith DV}, Murty VP (2022). Decision uncertainty during hypothesis testing enhances memory accuracy for incidental information. \textit{Learning \& Memory}, 29, 93-99. \doi{https://doi.org/10.1101/lm.053458.121}

[43] Tepfer LJ†, Alloy LB, \textbf{Smith DV} (2021). Family History of Depression is Associated with Alterations in Task-Dependent Connectivity between the Cerebellum and Ventromedial Prefrontal Cortex. \textit{Depression and Anxiety},  38(5), 508-520. \doi{https://doi.org/10.1002/da.23143} \neurovault{https://neurovault.org/collections/6130/} \materials{https://osf.io/ju32v/} \preregistration{http://aspredicted.org/blind.php?x=8qw2h3}

[42] Martins D, Rademacher L, Gabay AS, Taylor R, Richey JA, \textbf{Smith DV}, Gorlich KS, Nawijn L, Cremers HR, Wilson R, Bhattacharyya S, Paloyelis Y (2021). Mapping the brain areas underpinning social reward and punishment processing in the human brain: A voxel-based meta-analysis of neuroimaging findings using the Social Incentive Delay task. \textit{Neuroscience \& Biobehavioral Reviews}, 122, 1-17. \doi{https://doi.org/10.1016/j.neubiorev.2020.12.034} \neurovault{https://neurovault.org/collections/7793}

[41] Sazhin D†, Frazier A, Haynes CR†, Johnston C, Chat KY, Dennison JB†, Bart CP, McCloskey M, Chein J, Fareri DS, Alloy LB, Jarcho JM, \textbf{Smith DV} (2020). The Role of Social Reward and Corticostriatal Connectivity in Substance Use. \textit{Journal of Psychiatry and Brain Science}, 5:e200024. \doi{https://doi.org/10.20900/jpbs.20200024}

[40] Chen EY, Eickhoff S, Giovannetti T, \textbf{Smith DV} (2020). Reduced gray matter volume in the orbitofrontal cortex is associated with greater body mass index: a coordinate-based meta-analysis. \textit{NeuroImage: Clinical}, 28:102420. \doi{https://doi.org/10.1016/j.nicl.2020.102420} \neurovault{https://neurovault.org/collections/8703/} 

[39] Wang S†*, Tepfer LJ†*, Taren AA*, \textbf{Smith DV} (2020). Functional Parcellation of the Default Mode Network: A Large-Scale Meta-Analysis. \textit{Scientific Reports}, 10:16096. \doi{https://doi.org/10.1038/s41598-020-72317-8} \neurovault{https://identifiers.org/neurovault.collection:6262} \materials{https://zenodo.org/record/3599989\#.Xl2u4y2ZPOQ} 

[38] Botvinik-Nezer R, Holzmeister F, Camerer CF, Dreber A, Huber J, Johannesson M, Kirchler M, Iwanir R, Mumford JA, Adcock A, Avesani P, Baczkowski B, Bajracharya A, Bakst L, Ball S, Barilari M, Bault N, Beaton D, Beitner J, Benoit R, Berkers R, Bhanji J, Biswal B, Bobadilla-Suarez S, Bortolini T, Bottenhorn K, Bowring A, Braem S, Brooks H, Emily Brudner E, Calderon C, Camilleri J, Castrellon J, Cecchetti L, Cieslik E, Cole Z, Collignon O, Cox R, Cunningham W, Czoschke S, Dadi K, Davis C, De Luca A, Delgado MR, Demetriou L, Dennison JB†, Di X, Dickie E, Dobryakova E, Donnat C, Dukart J, Duncan NW, Durnez J, Eed A, Eickhoff S, Erhart A, Fontanesi L, Fricke GM, Galvan A, Gau R, Genon S, Glatard T, Glerean E, Goeman J,  Golowin S, González-García S, Gorgolewski K, Grady C, Green M, Guassi Moreira J, Guest O, Hakimi S, Hamilton JP, Hancock R, Handjaras G, Harry B, Hawco C, Herholz P, Herman G, Heunis S, Hoffstaedter F, Hogeveen J, Holmes S, Hu C, Huettel SA, Hughes M, Iacovella V, Iordan A, Isager P, Isik AI, Jahn A, Johnson M, Johnstone T, Joseph M, Juliano A, Kable J, Kassinopoulos M, Koba C, Kong X, Koscik T, Kucukboyaci NE, Kuhl B, Kupek S, Laird A, Lamm C, Langner R, Lauharatanahirun N, Lee H, Lee S, Leemans A, Leo A, Lesage E, Li F, Li M, Lim PC, Lintz E, Liphardt S, Losecaat Vermeer A, Love B, Mack M, Malpica N, Marins T, Maumet C, McDonald K, McGuire J, Melero H, Méndez Leal A, Meyer B, Meyer K, Mihai P, Mitsis G, Moll J, Nielson D, Nilsonne G, Notter M, Olivetti E, Onicas A, Papale P, Patil K, Peelle JE, Pérez A, Pischedda D, Poline JB, Prystauka Y, Ray S, Reuter-Lorenz P, Reynolds R, Ricciardi E, Rieck J, Rodriguez-Thompson A, Romyn A, Salo T, Samanez-Larkin GR, Sanz-Morales E, Schlichting M, Schultz D, Shen Q, Sheridan M, Shiguang F, Silvers J, Skagerlund K, Smith A, \textbf{Smith DV}, Sokol-Hessner P, Steinkamp S, Tashjian S, Thirion B, Thorp J, Tinghög G, Tisdall L, Tompson S, Toro-Serey C, Torre J, Tozzi L, Truong V, Turella L, van’t Veer AE, Verguts T, Vettel J, Vijayarajah S, Vo K, Wall M, Weeda WD, Weis S, White D, Wisniewski D, Xifra-Porxas A, Yearling E, Yoon S, Yuan R, Yuen K, Zhang L, Zhang X, Zosky J, Nichols TE, Poldrack RA, Schonberg T (2020). Variability in the analysis of a single neuroimaging dataset by many teams. \textit{Nature}, 582, 84-88. \doi{https://doi.org/10.1038/s41586-020-2314-9} \neurovault{https://neurovault.org/collections/6047/} \materials{https://github.com/poldrack/narps} \data{https://openneuro.org/datasets/ds001734/versions/1.0.4} 

[37] Fareri DS, \textbf{Smith DV}, Delgado MR (2020). The role of relationship closeness on network connectivity during trust-based interactions. \textit{Social Cognitive and Affective Neuroscience}, 15(3), 261-271. \doi{https://doi.org/10.1093/scan/nsaa031} 

[36] Wang Y*, Metoki A*, \textbf{Smith DV}, Medaglia JD, Zang Y, Benear S, Popal H, Lin Y, Olson IR (2020). Multimodal Mapping of the Face Connectome. \textit{Nature Human Behaviour}, 4, 397-411. \doi{https://doi.org/10.1038/s41562-019-0811-3}

[35] Butler PD, Hoptman MJ, \textbf{Smith DV}, Ermel JA, Calderone DC, Lee SH, Barch DM (2020). Grant Report on Social Reward Learning in Schizophrenia. \textit{Journal of Psychiatry and Brain Science}, 5:e200004. \doi{https://doi.org/10.20900/jpbs.20200004}

[34] Ng TH†, Alloy LB, \textbf{Smith DV} (2019). Meta-analysis of Reward Processing in Major Depressive Disorder Reveals Distinct Abnormalities within the Reward Circuit. \textit{Translational Psychiatry}, 9(293). \doi{https://doi.org/10.1038/s41398-019-0644-x} \neurovault{https://neurovault.org/collections/3884/} \materials{https://osf.io/sjb4d}

[33] Diehl MM, Lempert K, Parr AC, Ballard I, Steele VR, \textbf{Smith DV} (2018). Toward an Integrative Perspective on the Neural Mechanisms Underlying Persistent Maladaptive Behaviors. \textit{European Journal of Neuroscience}, 48(3), 1870-1883. \doi{https://doi.org/10.1111/ejn.14083}

[32] Utevsky AV, \textbf{Smith DV}, Young JS, Huettel SA (2017). Large-Scale Network Coupling with the Fusiform Cortex Future Social Motivation. \textit{eNeuro}, 4(5): eneuro.0084-17.2017. \doi{https://doi.org/10.1523/ENEURO.0084-17.2017} \neurovault{https://neurovault.org/collections/4804/}

[31] Li R*, \textbf{Smith DV}*, Clithero JA, Venkatraman V, Carter RM, Huettel SA (2017). Reason’s Enemy is Not Emotion: Engagement of Cognitive Control Networks Explain Biases in Gain/Loss Framing. \textit{Journal of Neuroscience}, 37 (13) 3588-3598. \doi{https://doi.org/10.1523/JNEUROSCI.3486-16.2017} \neurovault{http://neurovault.org/collections/1484/}

[30] \textbf{Smith DV} \& Delgado MR (2017). Meta-Analysis of Psychophysiological Interactions: Revisiting Cluster-Level Thresholding and Sample Sizes. \textit{Human Brain Mapping}, 38(1), 588-591. \doi{https://doi.org/10.1002/hbm.23354} \neurovault{https://neurovault.org/collections/1406/}

[29] Cho C, \textbf{Smith DV}, Delgado MR (2016). Reward Sensitivity Enhances Ventrolateral Prefrontal Cortex Activation During Free Choice. \textit{Frontiers in Neuroscience}, 10:529. \doi{https://doi.org/10.3389/fnins.2016.00529} \neurovault{http://neurovault.org/collections/2132}

[28] \textbf{Smith DV}, Gseir M, Speer ME, Delgado MR (2016). Toward a Cumulative Science of Functional Integration: a Meta-Analysis of Psychophysiological Interactions. \textit{Human Brain Mapping}, 37(8), 2904-17. \doi{https://doi.org/10.1002/hbm.23216} \neurovault{https://neurovault.org/collections/1406/}

[27] \textbf{Smith DV}, Rigney AE, Delgado MR (2016). Distinct Reward Properties are Encoded via Corticostriatal Interactions. \textit{Scientific Reports}, 6, 20093. \doi{https://doi.org/10.1038/srep20093} \neurovault{http://neurovault.org/collections/1408}

[26] Wang KS, \textbf{Smith DV}, Delgado MR (2016). Using fMRI to Study Reward Processing in Humans: Past, Present, and Future. \textit{Journal of Neurophysiology}, 115, 1664-1678. \doi{https://doi.org/10.1152/jn.00333.2015}

[25] \textbf{Smith DV}*, Sip KE*, Delgado MR (2015). Functional Connectivity with Distinct Neural Networks Tracks Fluctuations in Gain/Loss Framing Susceptibility. \textit{Human Brain Mapping}, 36(7), 2743-55. \doi{https://doi.org/10.1002/hbm.22804}

[24] Young JS*, \textbf{Smith DV}*, Coutlee CG, Huettel SA (2015). Synchrony Between Sensory and Cognitive Networks is Associated with Subclinical Variation in Autistic Traits. \textit{Frontiers in Human Neuroscience}, 9:146. \doi{https://doi.org/10.3389/fnhum.2015.00146} \neurovault{https://neurovault.org/collections/4805/}

[23] Sip KE, \textbf{Smith DV}, Porcelli AJ, Kar K, Delgado MR (2015). Social Closeness and Feedback Modulate Susceptibility to the Framing Effect. \textit{Social Neuroscience}, 10(1), 35-45. \doi{https://doi.org/10.1080/17470919.2014.944316}

[22] \textbf{Smith DV} \& Delgado MR (2015). Social Nudges: Utility Conferred from Others. \textit{Nature Neuroscience}, 18(6), 791-792. \doi{https://doi.org/10.1038/nn.4031}

[21] Murty VP, Shermohammed M, \textbf{Smith DV}, Carter RM, Huettel SA, Adcock RA (2014). Resting State Networks Distinguish Human Ventral Tegmental Area from Substantia Nigra. \textit{NeuroImage}, 100(1), 580-589. \doi{https://doi.org/10.1016/j.neuroimage.2014.06.047} \neurovault{http://neurovault.org/collections/2485/}

[20] \textbf{Smith DV}, Utevsky AV, Bland AR, Clement NJ, Clithero JA, Harsch AE, Carter RM, Huettel SA (2014). Characterizing Individual Differences in Functional Connectivity Using Dual-Regression and Seed-Based Approaches. \textit{NeuroImage}, 95(1), 1-12. \doi{https://doi.org/10.1016/j.neuroimage.2014.03.042}

[19] \textbf{Smith DV}, Clithero JA, Boltuck SE, Huettel SA (2014). Functional Connectivity with Ventromedial Prefrontal Cortex Reflects Subjective Value for Social Rewards. \textit{Social Cognitive and Affective Neuroscience}, 9(12), 2017-2025. \doi{https://doi.org/10.1093/scan/nsu005}

[18] Utevsky AV, \textbf{Smith DV}, Huettel SA (2014). Precuneus is a Functional Core of the Default-Mode Network. \textit{Journal of Neuroscience}, 34(3), 932-940. \doi{https://doi.org/10.1523/JNEUROSCI.4227-13.2014}

[17] Karnath H-O \& \textbf{Smith DV} (2014). The Next Step in Modern Brain Lesion Analysis: Multivariate Pattern Analysis. \textit{Brain}, 137(9), 2405-2407. \doi{https://doi.org/10.1093/brain/awu180}

[16] Strauman TJ, Detloff AM, Sestokas R, \textbf{Smith DV}, Goetz EL, Rivera C, Kwapil L (2013). What Shall I Be, What Must I Be: Neural Correlates of Personal Goal Activation. \textit{Frontiers in Integrative Neuroscience}, 6:123. \doi{https://doi.org/10.3389/fnint.2012.00123}

[15] \textbf{Smith DV}, Clithero JA, Rorden C, Karnath H-O (2013). Decoding the Anatomical Network of Spatial Attention. \textit{Proceedings of the National Academy of Sciences of the USA}, 110(4), 1518-1523. \doi{https://doi.org/10.1073/pnas.1210126110}

[14] Jelsone-Swain L, \textbf{Smith DV}, Baylis GC (2012). The Effect of Stimulus Duration and Motor Response in Hemispatial Neglect During a Visual Search Task. \textit{PLoS ONE}, 7(5), e37369. \doi{https://doi.org/10.1371/journal.pone.0037369}

[13] Libedinsky C, \textbf{Smith DV}, Teng CS, Namburi P, Chen V, Huettel SA, Chee MLW (2011). Sleep Deprivation Alters Valuation Signals in the Ventromedial Prefrontal Cortex. \textit{Frontiers in Behavioral Neuroscience}, 5:70. \doi{https://doi.org/10.3389/fnbeh.2011.00070}

[12] Clithero JA, Reeck CC, Carter RM, \textbf{Smith DV}, Huettel SA (2011). Nucleus Accumbens Mediates Relative Motivation for Rewards in the Absence of Choice. \textit{Frontiers in Human Neuroscience}, 5:87. \doi{https://doi.org/10.3389/fnhum.2011.00087}

[11] Bland AR, Mushtaq F, \textbf{Smith DV} (2011). Exploiting Trial-to-Trial Variability in Multimodal Experiments. \textit{Frontiers in Human Neuroscience}, 5:80. \doi{https://doi.org/10.3389/fnhum.2011.00080}

[10] Appelbaum LG, \textbf{Smith DV}, Boehler CN, Wen C, Woldorff MG (2011). Rapid Modulation of Sensory Processing Induced by Stimulus Conflict. \textit{Journal of Cognitive Neuroscience}, 23(9), 2620-2628. \doi{https://doi.org/10.1162/jocn.2010.21575 }

[9] Clithero JA, \textbf{Smith DV}, Carter RM, Huettel SA (2011). Within- and Cross-Participant Classifiers Reveal Different Neural Coding of Information. \textit{NeuroImage}, 56(2), 699-708. \doi{https://doi.org/10.1016/j.neuroimage.2010.03.057}

[8] \textbf{Smith DV} \& Huettel SA (2010). Decision Neuroscience: Neuroeconomics. \textit{Wiley Interdisciplinary Reviews: Cognitive Science}, 1(6), 854-871. \doi{https://doi.org/10.1002/wcs.73}

[7] Hayden BY, \textbf{Smith DV}, Platt ML (2010). Cognitive Control Signals in Posterior Cingulate Cortex. \textit{Frontiers in Human Neuroscience}, 4:223. \doi{https://doi.org/10.3389/fnhum.2010.00223}

[6] \textbf{Smith DV}, Davis B, Niu K, Healy E, Bonilha L, Fridriksson J, Morgan P, Rorden C (2010). Spatial Attention Evokes Similar Activation Patterns for Visual and Auditory Stimuli. \textit{Journal of Cognitive Neuroscience}, 22(2), 347-361. \doi{https://doi.org/10.1162/jocn.2009.21241 }

[5] \textbf{Smith DV}, Hayden BY, Truong T-K, Song AW, Platt ML, Huettel SA (2010). Distinct Value Signals in Anterior and Posterior Ventromedial Prefrontal Cortex. \textit{Journal of Neuroscience}, 30(7), 2490-2495. \doi{https://doi.org/10.1523/JNEUROSCI.3319-09.2010}

[4] Hayden BY, \textbf{Smith DV}, Platt ML (2009). Electrophysiological Correlates of Default-Mode Processing in Macaque Posterior Cingulate Cortex. \textit{Proceedings of the National Academy of Sciences of the USA}, 106(14), 5948-5953. \doi{https://doi.org/10.1073/pnas.0812035106}

[3] \textbf{Smith DV} \& Clithero JA (2009). Manipulating Executive Function with Transcranial Direct Current Stimulation. \textit{Frontiers in Integrative Neuroscience}, 3:26. \doi{https://doi.org/10.3389/neuro.07.026.2009}

[2] Clithero JA \& \textbf{Smith DV} (2009). Reference and Preference: How Does the Brain Scale Subjective Value? \textit{Frontiers in Human Neuroscience}, 3:11. \doi{https://doi.org/10.3389/neuro.09.011.2009}

[1] Almor A, \textbf{Smith DV}, Bonilha L, Fridriksson J, Rorden C (2007). What is in a Name? Spatial Brain Circuits are Used to Track Discourse References. \textit{Neuroreport}, 18(12), 1215-1219. \doi{https://doi.org/10.1097/WNR.0b013e32810f2e11} \\

\end{hangparas}



\subsection*{Books, Chapters, and Other Published Work}


\begin{hangparas}{.5in}{1}


[6] \textbf{Smith DV} and Huettel SA (2026, forthcoming). Functional MRI (fMRI). In G. Tranter and D. Le Pevelen (Eds.) \textit{Encyclopedia of Spectroscopy and Spectrometry}, 4th edition.

[5]  \textbf{Smith DV}, Lockwood P, Fareri DS (Eds.). (2025). \textit{Neuroeconomics: Core Topics and Current Directions}. Springer Nature.

[4] Wyngaarden J, Giovannetti T, Krekelberg B, \textbf{Smith DV} (2025). Maladaptive decision making in older adults: Confirmation bias and financial exploitation. In D. V. Smith, P. Lockwood, D. S. Fareri (Eds.), \textit{Neuroeconomics: Core Topics and Current Directions}. Springer Nature. Preprint available on \psyarxiv{https://osf.io/preprints/psyarxiv/abnyd}

[3] Ludwig RM† \& \textbf{Smith DV} (2023). Financial Fraud among Older Americans: Evidence and Implications. \textit{Temple University Public Policy Lab, Policy Brief}, 20, 1-5. \doi{https://doi.org/10.31234/osf.io/9f8ha}

[2] Bhanji JP, \textbf{Smith DV}, Delgado MR (2016). A Brief Anatomical Sketch of Human Ventromedial Prefrontal Cortex. [Supplementary Note 1 for Delgado et al. (2016). \textit{Nature Neuroscience}, 19(12), 1545-1552]. \doi{https://doi.org/10.31234/osf.io/zdt7f} \neurovault{https://neurovault.org/collections/5631/}

[1] \textbf{Smith DV} \& Delgado MR (2015). Reward Processing. In A. W. Toga (Ed.), \textit{Brain Mapping: An Encyclopedic Reference} (1st ed., pp. 361-366). Waltham, MA: Academic Press. Open access postprint on \psyarxiv{https://doi.org/10.31234/osf.io/b3gea}. \doi{https://doi.org/10.1016/B978-0-12-397025-1.00255-4} \\

\end{hangparas}


%\vspace{.4cm}
\section*{Invited Talks and Symposia}
\begin{hangparas}{.5in}{1}

\years{2024} Neural Responses to Social and Economic Decisions in the Aging Brain. University of Notre Dame.

\years{2024} Age-Related Differences in Neural Responses to Social Rewards: Risk Factors for Financial Exploitation and Cognitive Decline? Society for the Quantitative Analyses of Behavior in Philadelphia, PA.

\years{2024} Age-Related Differences in Neural Responses to Social and Economic Decisions. Ohio State University. 

\years{2024} Age-Related Differences in Neural Responses to Social and Economic Decisions. Rutgers University -- Newark. 

\years{2022} Age-related Differences in Social and Economic Decision Making. Society for Social Neuroscience in San Diego, CA.

\years{2020} Symposium on ``The Neuroscience of Decision Making in Organizations'' (panelist), Academy of Management in Vancouver, Canada. [canceled due to COVID-19]

\pagebreak

\years{2020} Social Decision Making in Older Adults: Risk Factors for Financial Exploitation? Scientific Research Network on Decision Neuroscience and Aging in Kapolei, Hawaii.

\years{2020} Neurocognitive Mechanisms of Social Decision Making in Older Adults. University of Hawaii at Manoa.

\years{2018} Constructing Value: Understanding the Role of Corticostriatal Connectivity. Symposium on Biology of Decision-Making in Paris, France.

\years{2017} Social and Economic Rewards Enhance Connectivity between the Ventral Striatum and the Default Mode Network. Rutgers University---Camden.

\years{2016} Brain Connectivity Shapes Responses to Social and Economic Incentives. The Nathan S. Kline Institute for Psychiatric Research, New York University.

\years{2016} Neural Circuitry Underlying Social and Economic Incentives. Temple University.

\years{2015} Neural Circuitry Underlying Social and Economic Incentives. Bard College.

\years{2015} Characterizing Individual Differences in Brain Connectivity. Kessler Foundation.

\years{2015} Linking Neural Circuits to Social and Economic Incentives: From Valuation to Outcome. Dartmouth College.

\years{2015} Interacting Brain Regions Contribute to a Range of Individual Differences. Kessler Foundation.

\years{2014} Advanced Statistical Procedures in Lesion Analysis: Multivariate Pattern Analysis. Federation of the European Societies of Neuropsychology Summer School in Berlin, Germany.

\years{2014} Characterizing Individual Differences in Decision Making. Sackler Institute for Developmental Psychobiology, Weill Medical College of Cornell University.

\years{2011} Neural Mechanisms of Social Valuation. Rutgers University---Newark.

\years{2011} Neural Mechanisms of Social Valuation. University of South Carolina.

\years{2010} Using FSL for Basic and Advanced Neuroimaging Analyses. Georgia State University / Georgia Tech Center for Advanced Brain Imaging. \\

\end{hangparas}


 %\SERVICE}
\section*{Service and Professional Activities}

\subsection*{Journal Reviewing and Editorial Roles}
\years{2022-present}Associate Editor, \textit{Collabra: Psychology}. \\
\years{2018-2023}Academic Editor, \textit{PLoS ONE}. \\
\years{2015-2017}Review Editor, \textit{Frontiers in Psychology}, section Decision Neuroscience. \\
\years{2015-2017}Review Editor, \textit{Frontiers in Neuroscience}, section Decision Neuroscience. \\


Ad Hoc Reviewer for 97 journals:
\begin{multicols}{2}
\begin{itemize}[noitemsep]
\itshape


\item Accountability in Research: Ethics, Integrity and Policy
\item Acta Psychologia
\item Addiction
\item Advanced Science
\item Advances in Methods and Practices in Psychological Science
\item AIMS Neuroscience
\item Annals of General Psychiatry
\item Annals of the New York Academy of Sciences
\item Biological Psychiatry
\item Biological Psychology
\item Behavioral and Brain Functions
\item Behavioral Neuroscience
\item Brain
\item Brain and Behavior
\item Brain Communications
\item Brain Imaging and Behavior
\item Brain Structure and Function
\item Brain Sciences
\item British Journal of Pharmacology
\item British Journal of Psychology
\item BMC Neuroscience 
\item Business and Society Review
\item Cell Reports
\item Cerebral Cortex 
\item Cognition
\item Cognitive, Affective, and Behavioral Neuroscience 
\item Collabra: Psychology
\item Communications Biology
\item Communications Psychology
\item Communications Medicine 
\item Cortex
\item Current Directions in Psychological Science
\item Current Neuropharmacology
\item Current Opinion in Behavioral Sciences
\item Developmental Cognitive Neuroscience 
\item Developmental Neuroscience 
\item Drug and Alcohol Dependence
\item Ecological Economics
\item European Journal of Neurology
\item European Journal of Neuroscience
\item Frontiers in Human Neuroscience 
\item Frontiers in Neuroinformatics 
\item Frontiers in Neurology 
\item Frontiers in Neuroscience 
\item Frontiers in Psychology 
\item Human Brain Mapping 
\item IEEE Transactions on Biomedical Engineering
\item IEEE Transactions on Neural Systems \& Rehabilitation Engineering
\item Imaging Neuroscience
\item International Journal of Consumer Studies
\item International Journal of Environmental Research and Public Health
\item International Journal of Hyperthermia 
\item International Journal of Innovation Studies
\item Journal of Cognitive Neuroscience 
\item Journal of Experimental Psychology: General
\item Journal of Genetic Psychology
\item The Journals of Gerontology, Series B: Psychological Sciences and Social Sciences
\item Journal of Integrative Medicine 
\item Journal of Integrative Neuroscience 
\item Journal of Medical Internet Research
\item Journal of Neurophysiology
\item Journal of Neuroscience 
\item Journal of Neuroscience, Psychology, \& Economics
\item Journal of Neuroscience Research
\item Journal of Psychiatric Research
\item Journal of Social and Personal Relationships
\item Management Information Systems Quarterly 
\item Nature Communications 
\item Nature Human Behaviour 
\item Nature Neuroscience
\item NeuroImage 
\item Neuroimage: Clinical 
\item Neurological Research
\item Neuropsychologia 
\item Neuropsychopharmacology 
\item Neuroscience Applied
\item Neuroscience Insights
\item Neuroscience Research 
\item npj Aging
\item Personality and Social Psychology Bulletin
\item PLoS Biology 
\item PLoS Computational Biology 
\item PLoS Digital Health 
\item PLoS ONE 
\item PNAS
\item PNAS Nexus
\item Psychological Medicine 
\item Psychological Reports
\item Psychological Science 
\item Psychopathology 
\item Psychophysiology
\item Quantitative Imaging in Medicine and Surgery
\item Scientific Reports 
\item Sleep
\item Social, Cognitive, and Affective Neuroscience 
\item Social Neuroscience
\item Translational Psychiatry
\item WIRES: Cognitive Science
\end{itemize}
\end{multicols}

\aiPublons \hspace{.05cm} \href{https://publons.com/author/1204254/david-v-smith}{publons.com} contains complete reviewing and editing record. \\ [.2cm]
Awards on \textit{Publons}: Top Reviewers for Neuroscience \& Behavior (2018); Top Reviewers for Multidisciplinary (2018); Top Reviewers for Temple University (2017); Top Reviewers for Neuroscience (2017).


\subsection*{Ad Hoc Grant Reviewing}
\years{2024} National Institutes of Health, ALP Study Section. \\
\years{2024} Deutsche Forschungsgemeinschaft (DFG) (German Research Foundation). \\
\years{2024} UK Research and Innovation, MRC Neurosciences and Mental Health. \\
\years{2023} Deutsche Forschungsgemeinschaft (DFG) (German Research Foundation). \\
\years{2021} German Academic Exchange Service (DAAD), PRIME Program. \\
\years{2020} National Institutes of Health, NPAS Study Section. \\
\years{2019} National Science Foundation, Social Psychology Program. \\
\years{2019} Mind Science Foundation. \\
\years{2018} National Science Foundation, Social Psychology Program. \\
\years{2018} Scientific Research Network on Decision Neuroscience \& Aging, Pilot Grants. \\
\years{2017} FWF Austrian Science Fund, START Program. \\
\years{2017} Swiss National Science Foundation, Humanities and Social Sciences, Division I. \\
\years{2017} Wellcome Trust, Senior Research Fellowship in Basic Biomedical Science. \\
\years{2015} Israel Science Foundation, Individual Research Grant. \\
\years{2014} Scientific Research Network on Decision Neuroscience \& Aging, Pilot Grants.

\subsection*{College and University Service at Temple University}
\years{2025-present} Public Policy Lab’s Advisory Board, College of Liberal Arts. \\ 
\years{2025-present} Teaching Awards Committee, College of Liberal Arts. \\ 
\years{2025-present} Budget Review Committee, Faculty Senate. \\
\years{2024-present} Tenure Track Merit Committee (elected), College of Liberal Arts. \\ 
\years{2024-present} Research Programs and Policies Committee (elected), Faculty Senate. \\
\years{2017} Subcommittee to evaluate and design deep learning server.

\subsection*{Departmental Service at Temple University}
\years{2024-present} Undergraduate Neuroscience Committee. \\
\years{2022-present} Faculty Awards Committee (Chair). \\ 
\years{2017-2022} Statistics Curriculum Committee. \\ 
\years{2021} Non-Clinical Graduate Area Reconfiguration Workgroup. \\
\years{2018-2022} Maladaptive Motivated Behaviors Seminar (Co-organizer with Dr. Mathieu Wimmer). \\
\years{2018-2019} Undergraduate Neuroscience Committee. \\
\years{2017-2020} Neuroimaging Methods Journal Club (Organizer). \\
\years{2017-2018} Faculty Search Committee in Social / Affective Neuroscience. \\
\years{2016-2017} Faculty Search Committee in Cognitive / Cognitive Neuroscience.



\subsection*{Society Memberships}
\begin{multicols}{2}
\begin{itemize}[noitemsep]
\item Association for Psychological Science
\item Cognitive Neuroscience Society
\item Eastern Psychological Association
\item New York Academy of Sciences
\item Organization for Human Brain Mapping
\item Social \& Affective Neuroscience Society
\item Society for Neuroeconomics
\item Society for Neuroscience
\item Society for Social Neuroscience
\item Society of Biological Psychiatry
\item Society for Judgment and Decision Making

\end{itemize}
\end{multicols}

\subsection*{Other Activities}
\begin{hangparas}{.5in}{1}
Co-Organizer, Duke University Neuroeconomics Journal Club (2008-2009).

Conference Abstract Reviewer: Organization for Human Brain Mapping (2010, 2013-2019, 2021, 2023, 2024); Cognitive Science Society (2017) Society for Neuroeconomics (2025). \\

\end{hangparas}


\years{2025-present} Best Practices Committee, Organization for Human Brain Mapping \\
\years{2025-present} Partnerships Committee, Social Affective Neuroscience Society \\



% ----------------------TEACHING------------------------------------------
\section*{Teaching and Mentoring Activities}
\subsection*{Teaching Experience}

\begin{hangparas}{.5in}{1}

[\underline{U}ndergraduate, \underline{G}raduate; \underline{S}pring, \underline{F}all; *original course]  \\

Instructor, \textit{Advanced Statistics} [G], Temple University: 2023S, 2024S, 2025S

Instructor, \textit{Topical Seminar in Neuroscience} [G], Temple University: 2022S\footnote{Topic: ``Neuroimaging Methods \& Analysis"}

Instructor, \textit{Current Topics in Neuroscience} [U], Temple University: 2019F\footnote{Cross-listed with \textit{Topics in Psychology}; Topic: ``Neuroimaging: From Image to Inference"}, 2025S\footnote{Topic: ``Neuroimaging: from image formation to statistical inference"}

Instructor, \textit{Decision Neuroscience}* [U], Temple University: 2019S, 2021S, 2023F, 2024F

Instructor, \textit{Foundations of Sensation and Perception} [U], Temple University: 2018F, 2020S, 2021S, 2021F, 2022S

Guest Lecturer, \textit{Advanced Neuroanatomy} [G], Lewis Katz School of Medicine, Temple University: 2018S

Instructor, \textit{Topics: Brain, Behavior and Cognition} [U], Temple University: 2017F\footnote{Topic: ``Decision Making and the Brain"}

Guest Lecturer, \textit{The Emotional Brain} [U], Rutgers University: 2014S

Lab Instructor, \textit{Neuroscience Boot Camp} [G], Duke University: 2011F

Teaching Assistant, \textit{Introduction to Cognitive Neuroscience} [U], Duke University: 2010S

Teaching Assistant, \textit
Supplemental Instruction Leader, \textit{Psychological Statistics} [U], University of South Carolina: 2006S

Teaching Assistant, \textit{Introductory Psychology} [U], University of South Carolina: 2005F, 2006S \\

\end{hangparas}


\subsection*{Mentoring}

\begin{tabbing}
Postdoctoral Fellows, as primary or co-primary mentor: \\  [.1cm]
\hspace{.5in} \= Dr. Jacob \= Stanley (2025-present). \\ 

\>  Dr. Rita Ludwig (2022-2023), \\ 
\> \> Data Scientist at UPenn. \\ [.9cm]


Graduate students, as primary or co-primary mentor: \\  [.1cm]
\> Farhad Shah (2025-present), Master's in Neuroscience (CNS), expected 2026 \\ 
\> Jamie-Nicole Luistro  (2025-present), Master's in Psychology (CNS), expected 2026 \\ 
\> Maraimi Sakhiashvili (2025-present), Master's in Neuroscience (CNS), expected 2026 \\ 
\> Derrick Dwamena (2024-present), Ph.D. in Psychology (CNS), expected 2029 \\ 
\> Shenghan Wang (2024-present, co-mentored with Chein), Ph.D. in Psychology (CNS), expected 2029 \\ 
\> Melanie Kos (2023-present, co-mentored with Helion), Ph.D. in Psychology (CNS), expected 2028 \\ 
\> Tia Tropea (2023-2024), Master's in Psychology, \\ 
\> \> Research Coordinator at UPenn. \\ 
\> James Wyngaarden (2020-present), Ph.D. in Psychology (Social), expected 2025 \\
\> Yi (Jen) Yang (2020-present), Ph.D. in Psychology (CNS), expected 2025 \\
\> Dr. Xinxu (Karen) Shen (2019-2024, co-mentored with Murty), Ph.D. in Psychology (CNS), \\
\> \> Postdoc at UC-Riverside. \\ 
\> Dr. Daniel Sazhin (2019-2024), Ph.D. in Psychology (CNS), \\
\> \> Postdoc at Air Force Research Laboratory. \\ 
\> Ezgi Kasimoglu (2019-2020), Master's in Neuroscience, \\ 
\> \> Research Assistant at Jefferson. \\
\> Dr. Jeffrey Dennison (2018-2023), Ph.D. in Psychology (CNS), \\
\> \> Postdoc at UPenn. \\ 
\> Lindsey Tepfer (2017-2020), Master's in Neuroscience \& Research Associate, \\
\> \> Ph.D. student at Dartmouth. \\ [.2cm]

Graduate students (other), as committee member or secondary mentor: \\  [.1cm]
\> Nicole Lalta (2025-present, Rutgers-Newark University) \\
\> Dr. Matthew Mattoni (2021-2025, Clinical Psychology) \\
\> Dr. Molly Tassoni (2024-2025, Clinical Psychology) \\
\> Dr. Talia Naiman (2025, Adelphi University) \\
\> Dr. David Gregory (2024, CNS) \\
\> Dr. Anne Walsh (2024, Social Psychology) \\
\> Dr. Elizabeth Horwath, (2023-2024, CNS) \\
\> Akanksha Nambiar (2023-present, University of West Bohemia) \\
\> Dr. Rachel Mis (2023, Clinical Psychology) \\
\> Dr. Rachel Myer (2022, CNS) \\
\> Dr. Elan French (2022, Clinical Psychology) \\
\> Dr. Haroon Popal (2021-2023, CNS) \\
\> Dr. Daniel Moriarity (2021, Clinical Psychology) \\
\> Dr. Katherine Hackett (2018-2023, Clinical Psychology) \\
\> Iris Chat (2018-2020, Clinical Psychology) \\
\> Dr. Corinne Bart (2019-2021, Clinical Psychology) \\
\> Dr. Tommy Ng (2017-2020, Clinical Psychology) \\
\> Nicole Henninger (2018-2019, Communications) \\
\> Dr. Sangsuk Yoon (2018, Business School) \\
\> Dr. William Hampton (2017-2018) \\
\> Dr. Ashley Drew (2017) \\
\> Dr. Kylie Alm (2017) \\
\> Dr. Gail Rosenbaum (2017) \\
\> Dr. Trishala Parthasarathi (2016-2017, University of Pennsylvania) \\ [.2cm]

%Undergraduates and post-baccalaureate research assistants: \\
Advisor for undergraduate independent study projects, internships, and research assistantships. Also \\
\> advisor for post-baccalaureate research assistants. Selected examples below: \\  [.1cm]

\> Cooper Sharp (research assistantship, '23-present), \\
\> Avi Dachs (research assistantship, '23-present), \\
\> Ori Zaff (research assistantship, '21-23), \\
\> \> Research Coordinator at UPenn. \\
\> Fatima Umar (Temple, '22), Neuroscience, \\
\> \> Medical Student at Drexel University. \\
\> Srikar Katta (Temple, '22), Honors Economics \& Data Science, \\
\> \> Ph.D. student at Duke. \\
\> John Marc Cipriaso (Temple, '20), Honors Psychology, \\
\> \> Medical Student at Lewis Katz School of Medicine, Temple University. \\
\> Victoria Kelly (research assistantship, '18-19). \\
\> Brijai Varma (visiting scholar, summer '18, '19), University of Pittsburgh. \\
\> Isaac Levy (visiting scholar, summer '18, spring '20), Oberlin College. \\
\> Benjamin Muzekari (Temple '19), Honors Psychology, \\
\> \> Ph.D. student UPenn. \\
\> Jane Gaisinsky (Temple '19), Neuroscience, \\
\> \> Research Assistant at UPenn. \\
\> Shaoming Wang (research assistantship, '17-18), \\
\> \> Ph.D. student at NYU. \\
\> Christian Reice (Temple, '17), Neuroscience, \\
\> \> Research Technician at CHOP.

\end{tabbing}

\begin{hangparas}{.5in}{1}
Prior trainees\footnote{These were individuals who I mentored in neuroimaging analysis while under the supervision of S. Huettel or M. Delgado.} with coauthored publications: Jacob S. Young (Duke undergrad); Sarah Boltuck (Duke undergrad); Amanda Utevsky (Duke grad); Rosa Li (Duke grad); Amy Bland (visiting Duke grad, from U of Manchester); Catherine Cho (Rutgers grad); K. Sally Wang (Rutgers grad); Mouad Gseir (Rutgers undergrad).
\end{hangparas}


\subsection*{Selected Student Awards}

\begin{hangparas}{.5in}{1}

Arunachalam Lakshmanan, Liberal Arts Undergraduate Research Award, for \textit{Understanding Social Reward and Self-Control in Online Gambling Risk} (Fall 2025).

Jamie-Nicole Luistro, Liberal Arts Undergraduate Research Award, for \textit{Environmental Stressors and Brain Health in Older Adults} (Spring 2025).

Jimmy Wyngaarden, National Research Service Award, for \textit{Characterizing the role of confirmation bias in financial exploitation of older adults} (2024-2027).

Ashley Hawk, Liberal Arts Undergraduate Research Award, for \textit{White Matter Hyperintensity Burden and Premature Brain Aging: Assessing Moderating Influences of Environmental Stressors and Social Support} (Fall 2024).

Ishika Kohli, Creative Arts, Research, and Scholarship Research Grant, for \textit{Understanding the Role of Anxiety in Planfulness Across the Lifespan} (Spring 2024).

Enes Yanilmaz, Liberal Arts Undergraduate Research Award, for \textit{Characterizing the Causal Influence of Noninvasive Brain Stimulation on Reward Processing} (Spring 2024).

Enes Yanilmaz, Creative Arts, Research, and Scholarship Travel Grant, for \textit{Age-related differences in neural responses to trust} (Fall 2023).

Matthew Drayton, Liberal Arts Undergraduate Research Award, for \textit{Characterizing Risk Factors for Financial Exploitation} (Fall 2023).

Cooper Sharp, Creative Arts, Research, and Scholarship Travel Grant, for \textit{Task-Dependent Functional Connectivity with the Cerebellum: Confounded by Nyquist Ghosting?} (Summer 2023).

Cooper Sharp, Liberal Arts Undergraduate Research Award, for \textit{The Signal and the Noise: Teasing Apart Cerebellar Responses to Decision-Making Tasks} (Spring 2023).

Ishika Kohli, Liberal Arts Undergraduate Research Award, for \textit{Age-Related Differences in Social and Economic Reward Processing} (Fall 2022).

Neriah Kahn, Liberal Arts Undergraduate Research Award, for \textit{Neural Mechanisms Underlying Social and Economic Reward Processing} (Spring 2022).

Srikar Katta, Creative Arts, Research, and Scholarship Research Grant, for \textit{Using Google Trends to Estimate the Effects of Disasters on Donations Behavior} (Fall 2021).

Scott Blender, Liberal Arts Undergraduate Research Award, for \textit{Causal Modeling of Corticostriatal Connectivity During Reward Processing} (Fall 2021).

Fatima Umar, Liberal Arts Undergraduate Research Award, for \textit{Meta-Analysis of Striatal Connectivity During Reward Processing} (Spring 2021).

Gemma Goldstein, Liberal Arts Undergraduate Research Award, for \textit{Shared Reward Processing and Substance Use} (Fall 2020). [declined due to COVID-19]

Gemma Goldstein, Liberal Arts Undergraduate Research Award, for \textit{Aberrant Reward Sensitivity: Mechanisms Underlying Substance Use} (Spring 2020). 

Srikar Katta, Liberal Arts Undergraduate Research Award, for \textit{The Neural Mechanisms of Risk Behavior} (Fall 2019).

Benjamin Muzekari, Liberal Arts Undergraduate Research Award, for \textit{Neural Mechanisms Underlying Social Decisions} (Spring 2019).

Benjamin Muzekari, Liberal Arts Undergraduate Research Award, for \textit{Modulating Perceptions of Fairness with Noninvasive Brain Stimulation} (Summer 2018).

Lindsey Tepfer, Career Development Grant, The American Association of University Women (2018-2019).

Jane Gaisinsky, Liberal Arts Undergraduate Research Award, for \textit{Modulating Deception with Noninvasive Brain Stimulation} (Spring 2018).

Jane Gaisinsky, Liberal Arts Undergraduate Research Award, for \textit{Altering Social Interactions with Noninvasive Brain Stimulation} (Fall 2017). \\

\end{hangparas}



% RECENT CONFERENCE PRESENTATIONS
%\vspace{.2cm}

\section*{Recent Conference Presentations (selected)}
\label{sec:conferences}

\subsection*{2025}
\begin{hangparas}{.5in}{1}

Dwamena D, Wyngaarden J, Kos M, Sharp C, Yang J, Jarcho J, Fareri D, \textbf{Smith DV} (April, 2025). Dorsal anterior cingulate responses to unreciprocated trust are associated with neural responses to unfairness. Poster presented at The Social \& Affective Neuroscience Society. Chicago, IL, USA

Kos M, Sazhin D, Yang Y, Mennis J, Helion C, \textbf{Smith DV} (April, 2025). Emotion regulation strategies moderate the association between anterior insula responses to fairness and relative deprivation. Poster presented at The Social \& Affective Neuroscience Society. Chicago, IL, USA.

Wyngaarden JB, Nambiar A, Dennison JB, Alloy LB, Fareri DS, Jarcho JM, \textbf{Smith DV} (April, 2025). Trait reward sensitivity and motivation shape connectivity between the default mode network and the striatum during reward anticipation. Poster presented at the Social \& Affective Neuroscience Society. Chicago, IL, USA.

O'Sullivan A, Dachs A, Sharp C, Skudlarek R, Mattheiss S, Zarabba J, Foster E, \textbf{Smith DV} (March, 2025). Preterm Birth and ADHD: Characterizing the Interactive Roles of Screentime, Neighborhood Disadvantage, and Social Support. Poster presented at the Eastern Psychological Association. New York, NY, USA.

Clarence H, Sharp C, Skudlarek R, Kos M, Mattheiss S, Mennis J, \textbf{Smith DV} (March, 2025). Does Area Deprivation Index moderate the relationship between Amygdala Reactivity and Social Support? Poster presented at the Eastern Psychological Association. New York, NY, USA.

\textbf{Smith DV} and Krekelberg B (February, 2025). tDCS over VLPFC modulates the exploit-explore tradeoff in a two-armed bandit task.  Poster presented at the Brain Stimulation meeting. Kobe, Japan. \\

\end{hangparas}



\subsection*{2024}
\begin{hangparas}{.5in}{1}

Yang Y, Sazhin D, Wyngaarden III JB, Clithero J, \textbf{Smith DV} (November, 2024). Evidence Accumulation Rate Mediates the Links between Decision Strategy and Decision Maker’s Reward Sensitivity and Trait Emotional Intelligence. Poster at the Society for Judgment and Decision Making meeting. New York, NY, USA.

Sazhin D, Chelsea H, Murty V, \textbf{Smith DV} (November, 2024). Effects of Trends in Information on Predictive Judgments. Poster presented at the Society for Judgment and Decision Making. New York, NY, USA.

Sharp CJ, Dachs A, Wyngaarden III J B, Sazhin D, Kohli I, Hawk A, Tropea T, Yanilmaz E, Jarcho J, Giovannetti T, Fareri DS, \textbf{Smith DV} (October, 2024). Age-related differences in neural responses to trust are associated with risk for financial exploitation. Poster presented at the Society for Neuroscience meeting. Chicago, IL, USA.

Wyngaarden JB, Sharp CJ, Dachs A, Sazhin D, Tropea T, Kohli I, Giovannetti T, Fareri DS, Jarcho JM, \textbf{Smith DV} (October, 2024). Risk for financial exploitation and psychosocial factors modulate age-related differences in social reward processing. Poster presented at the Society for Neuroscience meeting. Chicago, IL, USA.

Yttredahl A, \textbf{Smith DV}, Krekelberg B (June, 2024). tDCS over VLPFC increases reward sensitivity in a two-armed bandit task. Poster presented at the Organization for Human Brain Mapping meeting. Seoul, South Korea.

Wyngaarden III JB, Sharp CJ, Dachs A, Sazhin D, Tropea T, Kohli I, Giovannetti T, Fareri DS, Jarcho JM, \textbf{Smith DV} (April, 2024). Social support and risk for financial exploitation modulate age-related differences in reward processing. Poster presented at the Social and Affective Neuroscience Society meeting. Toronto, ON, Canada.

Yang Y, Kos MC, Dachs A, Sharp C, Wyngaarden III JB, Sazhin D, Tropea T, Kohli I, Hawk A, Giovannetti T, Fareri D, \textbf{Smith DV} (April, 2024). Emotion Regulation Strategies Moderate Age-related Differences in Corticostriatal Connectivity during Experiences of Shared Reward. Poster presented at the Social and Affective Neuroscience Society meeting. Toronto, ON, Canada.

Kos MC, Mitchell W, Wyngaarden III JB, Jarcho J, Fareri DS, \textbf{Smith DV}, Helion C (April, 2024). Representations of monetary and social feedback across social and non-social contexts. Poster presented at the Social and Affective Neuroscience Society meeting. Toronto, ON, Canada.

Kohli I, Tropea TR, Yang Y, Landes F, Jarcho JM, \textbf{Smith DV} (March, 2024). Understanding the Role of Anxiety in Planfulness Across the Lifespan. Poster presented at the Eastern Psychological Association Conference. Philadelphia, PA, USA.

Tropea TR, Sharp CJ, Dennison J, Mennis J, \textbf{Smith DV} (March, 2024). Understanding Age-Related Risk Behaviors: Neighborhoods, Socioeconomic Deprivation and Social Support. Poster presented at the Eastern Psychological Association Conference. Philadelphia, PA, USA. 

Hawk A, Kos M, Seifen C, Helion C, Giovannetti T, Mennis J, Fareri D, \textbf{Smith DV} (March, 2024). White matter hyperintensities and brain-age gap: Assessing environmental and social effects. Poster presented at the Eastern Psychological Association Conference. Philadelphia, PA, USA.

Tropea TR, Yang Y, Ludwig RM, Fareri DS, Mennis J, \textbf{Smith DV} (March, 2024). Financial Exploitation: Examining associations with Social Support, Need to Belong, and Community-level indicators of Social Cohesion. Poster presented at the American Psychology-Law Society Conference. Los Angeles, CA, USA. \\

\end{hangparas}


\subsection*{2023}
\begin{hangparas}{.5in}{1}

Sazhin D, Wyngaarden JB, Zaff O, Ludwig RM, Collins M, Sharp C, Dachs A, Nambiar A, Dennison JB, Drayton M, Tropea T, Clithero JA, Giovannetti T, \textbf{Smith DV} (November, 2023). Characterizing Age-Related Differences in Neural Responses During the Ultimatum Game. Poster presented at the Society for Neuroeconomics Meeting. Washington D.C., USA.

Dachs A, Sharp CJ, Yanilmaz E, Wyngaarden JB, Zaff O, Tropea T, Sazhin TD, Ludwig RM, Giovannetti T, Fareri DS, \textbf{Smith DV} (November, 2023). Examining Age-Related Differences in Neural Responses to Trust. Poster to be presented at the Society for Neuroscience Meeting. Washington D.C., USA.   

Wyngaarden JB, Zaff O, Sazhin D, Dachs A, Collins M, Johnston CR, Giovannetti T, Jarcho JM, \textbf{Smith DV} (November, 2023). Age-Related Differences in Social Reward Processing. Poster to be presented at the Society for Neuroscience Meeting. Washington D.C., USA.   

Yang Y, Zaff O, Wyngaarden JB, Dachs A, Sharp C, Collins MJ, Sazhin D, Ludwig RM, Giovanetti T, Fareri DS, \textbf{Smith DV} (November, 2023). Associations between Age and Neural Response to Reward in Social Contexts. Poster to be presented at the Society for Neuroscience Meeting. Washington D.C., USA.

De Arruda TCM, Johnston CR, Todorovski I, Wyngaarden JB, \textbf{Smith DV}, Jarcho JM (September, 2023). Childhood maltreatment and memory bias for social and non-social events: exploring neural mechanisms that promote risk for mental health problems. Poster presented at the Flux Society meeting. Santa Rosa, CA, USA. 

\textbf{Smith DV}, Dennison JB, Ori Zaff Z, Wyngaarden JB, Collins M, Dowdle L, Jarcho J, Olson I, Inglis B, Morgan P, Rorden C, Fareri DS (July, 2023). Characterizing the Effects of Multiecho and Multiband Imaging on Corticostriatal Responses to Reward. Poster presented at the Organization for Human Brain Mapping. Montreal, Canada.

Wyngaarden JB, Sharp CJ, Dennison JB, Sazhin D, Zaff O, Olson I, Fareri DS, Jarcho J, \textbf{Smith DV} (July, 2023). Task-Dependent Functional Connectivity with the Cerebellum is Confounded by Nyquist Ghosting. Poster presented at the Organization for Human Brain Mapping. Montreal, Canada.

Ruiz M, Gallardo S, Lima C, Sokol-Hessner P, \textbf{Smith DV}, Fareri DS (April, 2023). Choosing for others: neurocomputational mechanisms underlying risky choice. Poster presented at the Social and Affective Neuroscience meeting. Santa Barbara, CA, USA. \\


\end{hangparas}


\subsection*{2022}
\begin{hangparas}{.5in}{1}

Zaff O, Dennison JB, Sazhin D, Wyngaarden J, Vafiadis A, Collins M, Nguyen A, Chein J, Alloy L, Jarcho J, Fareri D, \textbf{Smith DV} (November, 2022). Individual differences in substance use are associated with elevated temporoparietal junction responses to rewards shared with friends. Poster presented at the Society for Neuroscience. San Diego, CA, USA.

Sazhin D, Dennison JB, Wyngaarden J, Zaff O, Vafiadis A, Kahn N, Collins M, Nguyen A, Kohli I, Fareri D, McCloskey M, Alloy L, Jarcho J, \textbf{Smith DV} (November, 2022). When Do We Choose to Be Fair? Strategic Choices in Bargaining Situations Are Associated with Elevated Corticostriatal Connectivity. Poster presented at the Society for Neuroscience. San Diego, CA, USA.

Ludwig RM, Dennison JB, Hackett K, Giovannetti T, Fareri DS, \textbf{Smith DV} (October, 2022). Older and Wiser? Young Adults and Seniors Respond Differently to Social Context in an Ultimatum Game. Poster presented at the Society for Neuroeconomics Meeting. Arlington, VA, USA.
 
Dennison JB, Umar F, Dachs A, \textbf{Smith DV} (October, 2022). Reward-Dependent Corticostriatal Connectivity: A Meta-analysis of Psychophysiological Interactions. Poster presented at the Society for Neuroeconomics Meeting. Arlington, VA, USA.

Sazhin D, Dennison J, Wyngaarden J, Vafiadis A, Zaff O, Kahn N, Collins M, Nguyen A, Kohli I., Fareri D, McCloskey M, Jarcho J, \textbf{Smith DV} (May, 2022). Strategic Decisions in Bargaining Situations Are Associated with Activation in the Caudate. Poster presented at the Social and Affective Neuroscience Society. [virtual meeting due to COVID-19]

Wyngaarden JB, Johnston CR, Sazhin D, Dennison JB, Vafiadis A., Zaff O, Kahn NA, Collins M, Nguyen A, Fareri D, McCloskey M, Alloy L, \textbf{Smith DV}, Jarcho JM (May, 2022). Alcohol use is associated with enhanced corticostriatal connectivity with precuneus during social reward. Poster presented at the Social and Affective Neuroscience Society. [virtual meeting due to COVID-19]

Yang Y, Hackett K, Katta S, Jarcho J, Giovannetti T, Fareri D, \textbf{Smith DV} (May, 2022). Risk for Financial Exploitation: Characterizing the Role of Socioeconomic Status, Cognition, and Social Decision Making. Poster presented at the Association for Psychological Science. Chicago, IL, USA.

Shen, X, Wang KS, Murty VP, \textbf{Smith DV} (May, 2022). Dissociable representations of affective and informative reward properties in the dorsal striatum. Poster presented at the Social and Affective Neuroscience Society. [virtual meeting due to COVID-19]

Ruiz M, Stasiak JE, Maldonado M, Kim D, Sokol-Hessner P, \textbf{Smith DV}, Fareri DS (May, 2022). Willingness-to-pay for social experiences: Social cognitive functioning relates to individuals' choices between social and non-social experiences. Poster presented at the Social and Affective Neuroscience Society. [virtual meeting due to COVID-19]

Shen X, \textbf{Smith DV}, Murty VP (April, 2022). The effect of curiosity on memory during anticipation and outcome phase. Poster presented at the Cognitive Neuroscience Society. San Francisco, CA, USA. \\

\end{hangparas}


\subsection*{2021}
\begin{hangparas}{.5in}{1}

Dennison JB \& \textbf{Smith DV} (September, 2021). Understanding How Individual Beliefs About Risk Contribute to Ambiguity Aversion. Poster presented at the Society for Neuroeconomics. [virtual meeting due to COVID-19]

Ruiz M, Stasiak JE, Sokol-Hessner P, \textbf{Smith DV}, Fareri DS (September, 2021). Willingness-to-pay for social experiences: How social cognitive functioning relates to individuals' choices between social and non-social experiences. Poster presented at the Society for Neuroeconomics. [virtual meeting due to COVID-19]

Sazhin D, Nguyen A, \textbf{Smith DV} (September, 2021). Meta-Analysis of Explore-Exploit Decisions Reveals Convergence in the Salience Network. Poster presented at the Society for Neuroeconomics. [virtual meeting due to COVID-19]

Shen X, \textbf{Smith DV}, Murty VP (August, 2021). Age- and anxiety-related influences of curiosity on free recall using an automated-machine learning scoring approach. Poster to be presented at CEMS. Philadelphia, PA, USA.

Sazhin D, Helion C, \textbf{Smith DV} (May, 2021). The Steeper the Curve, the Longer People Delay: Effect of Exponential Information on Decision Making. Poster presented at the Association for Psychological Science. [virtual meeting due to COVID-19]

Chat IK-Y, Bart C, Dennison J, \textbf{Smith DV}, Miller GE, Nusslock R, Alloy LB (May, 2021). Inflammatory Signaling and Corticostriatal Functional Connectivity to Anticipated Valence and Salience of Reward and Threat Stimuli: An Investigation in Depressed vs. Non-Depressed Young Adults. Poster presented at Society for Biological Psychiatry. [virtual meeting due to COVID-19]

Shen X, \textbf{Smith DV}, Murty VP (May, 2021). Machine learning as an automated approach to scoring Free Recall of Naturalistic Stimuli. Poster presented at Social Affective Neuroscience Society. [virtual meeting due to COVID-19]

Shen X, \textbf{Smith DV}, Murty VP (March 2021). Machine learning as an automated approach to scoring Free Recall of Naturalistic Stimuli. Poster presented at Cognitive Neuroscience Society. [virtual meeting due to COVID-19]

Hackett K, Katta S, Jarcho J, Fareri DS, Giovannetti T, \textbf{Smith DV} (February, 2021). Relationship between cognition, social support, and susceptibility to fraud among two groups of older adults before and during COVID-19. Poster presented at International Neuropsychology Society. [virtual meeting due to COVID-19] \\

\end{hangparas}

\subsection*{2020}
\begin{hangparas}{.5in}{1}

Jarcho J, Haynes C, Quarmley M, Johnston C, \textbf{Smith DV}, Cassidy C (December, 2020). Neuromelanin-Sensitive MRI Signal is Associated with Functional Striatal Response to Social but Not Monetary Reward Processing: Potential Mechanisms for Social Anxiety. Annual Meeting of the American College of Neuropsychopharmacology. [virtual meeting due to COVID-19]

Katta S, Hackett K, Jarcho JM, Giovannetti T, Fareri DS, \textbf{Smith DV} (October, 2020). Financial Exploitation in Older Adults: Characterizing the Role of Sociodemographic Factors, Cognition, and Social Decision Making. Poster presented at the 17th meeting of the Society for Neuroeconomics. [virtual meeting due to COVID-19]

Fareri DS, Hackett K, Giovannetti T, \textbf{Smith DV} (October, 2020). Older Adults Exhibit Enhanced Connectivity between Caudate and Default Mode Network During Shared Reward Processing. Poster presented at the 17th meeting of the Society for Neuroeconomics. [virtual meeting due to COVID-19]

Senia N, \textbf{Smith DV}, Fareri DS (March, 2020). Neural responses to drug induced cues in cocaine and heroin users: an activation likelihood meta-analysis. Poster presented at the 27th meeting of the Cognitive Neuroscience Society. Boston, MA, USA. [virtual meeting due to COVID-19]

O'Shea I, \textbf{Smith DV}, Murty V (March, 2020). Differences in Resting-State Midbrain Connectivity in Parkinson’s Disease. Poster presented at the 27th meeting of the Cognitive Neuroscience Society. Boston, MA, USA. [virtual meeting due to COVID-19]

Shen X, Murty V, \textbf{Smith DV} (March, 2020). Actively testing hypothesis using acquired information during encoding enhances delayed memory. Poster presented at the 27th meeting of the Cognitive Neuroscience Society. Boston, MA, USA. [virtual meeting due to COVID-19]

Chen EY, Giovannetti T, \textbf{Smith DV} (June, 2020). Obesity is associated with reduced orbitofrontal cortex volume: a coordinate-based meta-analysis. Poster presented at the 26th meeting of the Organization for Human Brain Mapping, Montreal, Canada. [virtual meeting due to COVID-19] \\

\end{hangparas}


\subsection*{2019}
\begin{hangparas}{.5in}{1}

Tepfer LJ, Alloy LB, \textbf{Smith DV} (October, 2019). Familial and lifetime history of depression: alterations in the neural circuitry underlying reward and social cognition. Poster presented at the 50th meeting of the Society for Neuroscience. Chicago, IL, USA.

Hackett K, Henninger NM, Kelly V, Giovannetti T, Fareri DS, \textbf{Smith DV} (October, 2019). Response to perceived fairness is associated with reduced connectivity within reward circuitry in older adults. Poster presented at the 50th meeting of the Society for Neuroscience. Chicago, IL, USA.

Kelly V, Hackett K, Henninger NM, Giovannetti T, \textbf{Smith DV}, Fareri DS (October, 2019). Aging alters corticostriatal interactions during shared reward processing. Poster presented at the 50th meeting of the Society for Neuroscience. Chicago, IL, USA.

\textbf{Smith DV}, Liu Y, Krekelberg B (October, 2019). Transcranial alternating current stimulation alters reward-dependent corticostriatal interactions. Poster presented at the 50th meeting of the Society for Neuroscience. Chicago, IL, USA. 

Henninger NM, Kelly V, Hackett K, Fareri DS, Tepfer LJ, Katta S, Reeck C, Giovannetti T, Beard EC, Dennison J, Muzekari B, Desalme DF, Kinmartin R, Lang A, Cipriaso JM, Hunter E, Morrison C, \textbf{Smith DV} (October, 2019). Age‐related reductions in functional connectivity in social brain systems during an economic trust task. Poster presented at the 50th meeting of the Society for Neuroscience. Chicago, IL, USA.

Dennison JB, Ng T, Alloy L, \textbf{Smith DV} (October, 2019). Using Corticostriatal Networks to Disentangle Reward Value and Salience. Poster presented at the 50th meeting of the Society for Neuroscience. Chicago, IL, USA.

\textbf{Smith DV}, Liu Y, Krekelberg B (October, 2019). Transcranial alternating current stimulation alters reward-dependent corticostriatal interactions. Poster presented at the 16th meeting of the Society for Neuroeconomics. Dublin, Ireland. 

Tepfer LJ, Slipenchuk M, Muzekari B, Krekelberg B, \textbf{Smith DV} (June, 2019). Altering Social Norm Compliance with Transcranial Alternating Current Stimulation. Poster presented at the 9th meeting of the Interdisciplinary Symposium on Decision Neuroscience. Durham, North Carolina, USA.

Kelly V, Slipenchuk M, Katta S, Clithero JA, \textbf{Smith DV} (June, 2019). The More the Merrier: Participants Value Having More Options to Choose From. Poster presented at the 9th meeting of the Interdisciplinary Symposium on Decision Neuroscience. Durham, North Carolina, USA.

Henninger NM, Katta S, Kelly V, Hackett K,  Reeck C, Giovannetti T, Fareri DS, \textbf{Smith DV} (June, 2019). Aging is associated with reductions in functional connectivity in social brain systems. Abstract presented at the annual Interdisciplinary Symposium on Decision Neuroscience. Durham, NC, USA.

Fareri DS, Kelly V, Henninger NM, Hackett K, DeSalme D, Muzekari B, Katta S, Reeck C, Giovannetti T, \textbf{Smith DV} (May 2019). The influence of close relationships on shared reward processing in older and younger adults. Poster presented at the 12th meeting of the Social \& Affective Neuroscience Society. Miami, FL, USA.

\textbf{Smith DV}, Henninger NM, Hackett K, Kelly V, DeSalme D, Muzekari B, Katta S, Giovannetti T, Fareri DS (June, 2019). Fairness is Associated with Increased Connectivity between the Executive Control Network and MPFC. Abstract submitted for consideration at the 25th meeting of the Organization for Human Brain Mapping. Rome, Italy.

Ng TH, Alloy LB, \textbf{Smith DV} (March, 2019). Reward Processing in Preadolescents with Bipolar Disorder: An fMRI Study. Abstract submitted for consideration at the 21st meeting of the International Society for Bipolar Disorders. Sydney, Australia.

Tepfer LJ, Slipenchuk M, Muzekari B, Krekelberg B, \textbf{Smith DV} (March, 2019). Altering Social Norm Compliance with Transcranial Alternating Current Stimulation. Poster presented at the 90th meeting of the Eastern Psychological Association. New York, New York, USA.

Muzekari B, Slipenchuk M, Tepfer LJ, Krekelberg B, \textbf{Smith DV} (March, 2019). Modulating Social Influences on Fairness Perception with Transcranial Alternating Current Stimulation. Poster presented at the 90th meeting of the Eastern Psychological Association. New York, New York, USA. \\

\end{hangparas}


\subsection*{2018}
\begin{hangparas}{.5in}{1}

Chiu M, Ng TH, Alloy LB, \textbf{Smith DV} (October, 2018). Linking Valuation Circuitry with Maladaptive Decision Making within the Human Connectome Project. Poster presented at the 16th meeting of the Society for Neuroeconomics. Philadelphia, PA, USA.

Chiu M, Ng TH, Alloy LB, \textbf{Smith DV} (May, 2018). Reward-dependent Connectivity with Orbitofrontal Cortex in Subclinical Depression. Poster presented at the 73rd meeting of the Society of Biological Psychiatry. New York, NY, USA.

Zhang H, Venkatraman V, \textbf{Smith DV} (May, 2018). Perceiving Social Interactions Suppresses Connectivity between the Default Mode Network and Ventral Striatum. Poster presented at the 11th meeting of the Social \& Affective Neuroscience Society. New York, NY, USA. \\

\end{hangparas}


\subsection*{2017}
\begin{hangparas}{.5in}{1}
Ng TH, Alloy LB, \textbf{Smith DV} (November, 2017). Reward Processing Abnormalities in Mood Disorders: A Systematic Review and Meta-analysis of Neuroimaging Studies. Poster presented at the 51st meeting of the Association for Behavioral and Cognitive Therapies. San Diego, CA, USA.

Ng TH, Alloy LB, \textbf{Smith DV} (October, 2017). Reward Processing Abnormalities in Unipolar Depression: A Meta-analysis of Neuroimaging Studies. Poster presented at the 15th meeting of the Society for Neuroeconomics. Toronto, ON, Canada.

Wang S, \textbf{Smith DV}, Delgado MR (September, 2017). Informative and Affective Neural Pathways underlying Explore-Exploit Tradeoffs. Poster presented at the inaugural Computational Cognitive Neuroscience conference. New York, NY, USA.

Dobryakova E \& \textbf{Smith DV} (June, 2017). Reward Enhances Connectivity between the Ventral Striatum and the Default Mode Network. Poster presented at the 23rd meeting of the Organization for Human Brain Mapping. Vancouver, BC, Canada.

Wang  S, Taren AA, \textbf{Smith DV} (May, 2017). Large-Scale Meta-Analytic Characterization of the Default Mode Network. Poster presented at the 29th meeting of the Association for Psychological Science. Boston, MA, USA.

Chen EY, Foster GD, Mohamed FB, Conklin CJ, Hoge WS, Olson IR, Chein JM, \textbf{Smith DV}, McCloskey MS, Obradović Z, Olino TM, and the Temple Eating Disorders program represented by Jean M. Arlt (May, 2017). Can Baseline Resting State Functional Connectivity Classify Clinically Significant Weight Loss 3 and 15 Months Later? Poster presented at the 29th meeting of the Association for Psychological Science. Boston, MA, USA.

Chen EY, Olson I, \textbf{Smith DV}, Olino T, McCloskey MS, Chein J, Edwards M, Obradovic Z  (April, 2017). The use of multivariate pattern analysis to develop and test an objective diagnostic clinical test for binge eating disorder in the context of obesity. Poster presented the 3rd meeting of the Association for Clinical and Translational Science. Washington, DC.

Fareri DS, \textbf{Smith DV}, Delgado MR (March, 2017). Reciprocation from a friend enhances coupling between the default mode network and ventral striatum. Talk given (by D. Fareri) at the 10th meeting of the Social \& Affective Neuroscience Society. Los Angeles, CA, USA. \\

\end{hangparas}


\subsection*{2016}
\begin{hangparas}{.5in}{1}
\textbf{Smith DV}, Wang S, Delgado MR (November, 2016). Neural Pathways Underlying Explore-Exploit Tradeoffs in Social and Nonsocial Contexts. Poster presented at the 7th meeting of the Society for Social Neuroscience. San Diego, CA, USA.

\textbf{Smith DV}, Wang S, Delgado MR (November, 2016). Neural Pathways Underlying Explore-Exploit Tradeoffs in Social and Nonsocial Contexts. Poster presented at the 46th meeting of the Society for Neuroscience. San Diego, CA, USA.

Li R, \textbf{Smith DV}, Clithero JA, Venkatraman V, Carter RM, Huettel SA (August, 2016). Revisiting the dual-systems model of choice using fMRI: Cognitive engagement and disengagement explain biases in gain/loss framing. Poster presented at the 14th meeting of the Society for Neuroeconomics. Berlin, Germany.

Utevsky AV, \textbf{Smith DV}, Venkatraman V, Huettel SA (August, 2016). Distinct subregions within the temporoparietal junction and posterior cingulate uniquely track prosocial decision-making. Poster presented at the 14th meeting of the Society for Neuroeconomics. Berlin, Germany.

Hakimi S, Clithero JA, Mullette-Gillman OA, \textbf{Smith DV}, McLaurin E, Taren A, Venkatraman V, Huettel SA, Carter RM (August, 2016). Decomposing Risk Representation in Parietal Cortex. Poster presented at the 14th meeting of the Society for Neuroeconomics. Berlin, Germany.

\textbf{Smith DV}, Li R, Clithero JA, Venkatraman V, Carter RM, Huettel SA (May, 2016). Revisiting the dual-systems model of choice using fMRI: Cognitive engagement and disengagement explain biases in gain/loss framing. Poster presented at the 28th meeting of the Association for Psychological Science. Chicago, IL, USA.

\textbf{Smith DV}, Gseir M, Speer ME, Delgado MR (April, 2016). Toward a Cumulative Science of Functional Integration: a Meta-Analysis of Psychophysiological Interactions. Poster presented at the 9th meeting of the Social \& Affective Neuroscience Society. New York, NY, USA.

\textbf{Smith DV}, Gseir M, Speer ME, Delgado MR (April, 2016). Toward a Cumulative Science of Functional Integration: a Meta-Analysis of Psychophysiological Interactions. Poster presented at the 10th annual Reprogramming the Brain to Health symposium. Dallas, TX, USA. \\

\end{hangparas}




\vspace{.5cm}
Please contact me directly for conference presentations prior to 2016. 




%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
{\scriptsize  Last updated: \today\- •\-
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{\XeTeX} •\- Source code on \href{https://github.com/DVSneuro/my-cv}{GitHub}\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
\href{https://liberalarts.temple.edu/sites/liberalarts/files/SmithDV\_vita.pdf}{https://liberalarts.temple.edu/sites/liberalarts/files/SmithDV\_vita.pdf}}
\end{center}

\end{document}